---
title: "Average Age of Members in Congress"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
library(ggplot2)
library(dplyr)
library(fivethirtyeight)

avg_congress_age <- congress_age %>%
  select(termstart, party, age) %>%
  group_by(termstart, party) %>%
  summarize(mean_age = mean(age)) %>%
  filter(party == "R"| party == "D")

avg_congress_age <- avg_congress_age %>%
  mutate(mean_age_months =(mean_age*12))
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
ggplot(avg_congress_age,aes(x=termstart, y=mean_age, factor=party, color=party))+geom_line()+
  ylim(40,60)+
  labs(title="Average Age of Members in Congress", subtitle="at start of term 1947-2013", x="date", y="average age")+
  scale_color_manual(values=c("D"="#0000ff", "R"="#ff0000"))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
